---
title: "Data generation"
output: html_notebook
---

Author : Purwoko Haryadi Santoso, UNY, Indonesia

# I. Import the employed packages
```{r}
library(GenOrd)
library(psych)
library(mirt)
```

# II. Data generation for 3-point categorical data

## A. Setting of marginal distribution for 3-point scale

```{r}
marginal_3 <- list(c(0.1, 0.6), 
                 c(0.1, 0.6), 
                 c(0.1, 0.6), 
                 c(0.1, 0.6),
                 c(0.1, 0.6),
                 c(0.1, 0.6),
                 c(0.1, 0.6),
                 c(0.1, 0.6),
                 c(0.1, 0.6),
                 c(0.1, 0.6))
```

## B. Correlation matrix among 10 items (controlled condition)

```{r}
k <- 10 # number of generated items
Sigma <- matrix(c(1,0.5,0.4,0.3,0.4,0.62,0.61,0.5,0.32,0.4,
                  0.5,1,0.5,0.4,0.3,0.4,0.62,0.61,0.5,0.32,
                  0.4,0.5,1,0.5,0.4,0.3,0.4,0.62,0.61,0.5,
                  0.3,0.4,0.5,1,0.5,0.4,0.3,0.4,0.62,0.61,
                  0.4,0.3,0.4,0.5,1,0.5,0.4,0.3,0.4,0.62,
                  0.62,0.4,0.3,0.4,0.5,1,0.5,0.4,0.3,0.4,
                  0.61,0.62,0.4,0.3,0.4,0.5,1,0.5,0.4,0.3,
                  0.5,0.61,0.62,0.4,0.3,0.4,0.5,1,0.5,0.4,
                  0.32,0.5,0.61,0.62,0.4,0.3,0.4,0.5,1,0.5,
                  0.4,0.32,0.5,0.61,0.62,0.4,0.3,0.4,0.5,1), k, k, byrow=TRUE)
```

## C. Data generation as many as 1000 replication (M)

```{r}
M <- 1000 # number of replication
n <- 1000 # sample size
set.seed(100) # set the "randomness" of the data
data_3 = list()

ptm <- proc.time() # to record the computation time

for(i in 1:M){
  data_3[[i]] <- ordsample(n, marginal_3, Sigma)
}

saveRDS(data_3, "output dataset/data_3.rds")

proc.time() - ptm # Stop
```

# III. Data generation for 5-point categorical data

## A. Setting of marginal distribution for 5-point scale

```{r}
marginal_5 <- list(c(0.2,  0.3,  0.5,  0.6), 
                 c(0.2,  0.3,  0.5,  0.6), 
                 c(0.2,  0.3,  0.5,  0.6), 
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6),
                 c(0.2,  0.3,  0.5,  0.6))
```

## B. Data generation as many as 1000 replication (M) with the same determined Sigma matrix

```{r}
set.seed(100)
data_5 = list()

ptm <- proc.time()

for(i in 1:M){
  data_5[[i]] <- ordsample(n, marginal_5, Sigma)
}

saveRDS(data_5, "output dataset/data_5.rds")

proc.time() - ptm
```

# IV. Data generation for 7-point categorical data

## A. Setting of marginal distribution for 7-point scale

```{r}
marginal_7 <- list(c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.9))
```

## B. Data generation as many as 1000 replication (M) with the same determined Sigma matrix

```{r}
set.seed(100)
data_7 = list()

ptm <- proc.time()

for(i in 1:M){
  data_7[[i]] <- ordsample(n, marginal_7, Sigma)
}

saveRDS(data_7, "output dataset/data_7.rds")

proc.time() - ptm
```

# V. Data generation for 9-point categorical data

## A. Setting of marginal distribution for 9-point scale

```{r}
marginal_9 <- list(c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9), 
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9),
                 c(0.1, 0.2,  0.3,  0.4, 0.5, 0.6, 0.7, 0.9))
```

## B. Data generation as many as 1000 replication (M) with the same determined Sigma matrix

```{r}
set.seed(100)
data_9 = list()

ptm <- proc.time()

for(i in 1:M){
  data_9[[i]] <- ordsample(n, marginal_9, Sigma)
}

saveRDS(data_9, "output dataset/data_9.rds")

proc.time() - ptm
```

# VI. Data generation for 11-point categorical data

## A. Setting of marginal distribution for 11-point scale

```{r}
marginal_11 <- list(c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), 
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), 
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), 
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9),
                 c(0.1, 0.2,  0.3,  0.35, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9))
```

## B. Data generation as many as 1000 replication (M) with the same determined Sigma matrix

```{r}
set.seed(100)
data_11 = list()

ptm <- proc.time()

for(i in 1:M){
  data_11[[i]] <- ordsample(n, marginal_11, Sigma)
}

saveRDS(data_11, "output dataset/data_11.rds")

proc.time() - ptm
```




