---
title: "GRM modeling"
output: html_notebook
---

Author : Purwoko Haryadi Santoso, UNY, Indonesia

# I. Open the five generated dataset (.RDS)
```{r}
data_3 <- readRDS("output dataset/data_3.rds")
data_5 <- readRDS("output dataset/data_5.rds")
data_7 <- readRDS("output dataset/data_7.rds")
data_9 <- readRDS("output dataset/data_9.rds")
data_11 <- readRDS("output dataset/data_11.rds")
```

# II. GRM modeling for 3-point (Warning : this will takes your time, prepare your hot coffee and monitor)
```{r, warning=FALSE}
library(mirt)
mod.grm_3 = list()

for(i in 1:1000){
  mod.grm_3[i] <- mirt(data.frame(data_3[[i]]), model=1, itemtype="graded")
}

saveRDS(mod.grm_3, "output GRM/mod.grm_3.rds")
```

# III. GRM modeling for 5-point (Warning : the greater point number, the longer computation will take !)
```{r, warning=FALSE}
mod.grm_5 = list()

for(i in 1:1000){
  mod.grm_5[i] <- mirt(data.frame(data_5[[i]]), model=1, itemtype="graded")
}

saveRDS(mod.grm_5, "output GRM/mod.grm_5.rds")
```

# IV. GRM modeling for 7-point
```{r, warning=FALSE}
mod.grm_7 = list()

for(i in 1:1000){
  mod.grm_7[i] <- mirt(data.frame(data_7[[i]]), model=1, itemtype="graded")
}

saveRDS(mod.grm_7, "output GRM/mod.grm_7.rds")
```

# V. GRM modeling for 9-point
```{r, warning=FALSE}
mod.grm_9 = list()

for(i in 1:1000){
  mod.grm_9[i] <- mirt(data.frame(data_9[[i]]), model=1, itemtype="graded")
}

saveRDS(mod.grm_9, "output GRM/mod.grm_9.rds")
```

# VI. GRM modeling for 9-point
```{r, warning=FALSE}
mod.grm_11 = list()

for(i in 1:1000){
  mod.grm_11[i] <- mirt(data.frame(data_11[[i]]), model=1, itemtype="graded")
}

saveRDS(mod.grm_11, "output GRM/mod.grm_11.rds")
```

# Additional code : extract item fit (chi square)

```{r, warning=FALSE}
itemfit_3 <- list()
itemfit_5 <- list()
itemfit_7 <- list()
itemfit_9 <- list()
itemfit_11 <- list()

for(i in 1:M){
  itemfit_3[[i]] <- itemfit(mod.grm_3[[i]])
  itemfit_5[[i]] <- itemfit(mod.grm_5[[i]])
  itemfit_7[[i]] <- itemfit(mod.grm_7[[i]])
  itemfit_9[[i]] <- itemfit(mod.grm_9[[i]])
  itemfit_11[[i]] <- itemfit(mod.grm_11[[i]])
}

itemfit <- list(itemfit_3, itemfit_5, itemfit_7, itemfit_9, itemfit_11)
saveRDS(itemfit, "output GRM/itemfit.rds")
```



